---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

### Package requiered: *base*
```{r echo="true"}
DT<-read.csv("activity.csv", header=T)
```


## What is mean total number of steps taken per day?

### Histogram total number of steps:

```{r echo="true"}
steps<-by(DT$steps, DT$date, function(x) sum(x))
hist(steps)

```

### Mean number of steps per day : `r mean(steps, na.rm="true")`
### Median number of steps per day `r median(steps, na.rm="true")`

## What is the average daily activity pattern?

```{r echo="true"}
dailyavg<-by(DT$steps, DT$interval, function(x) mean(x, na.rm="true"))
plot(dailyavg, type="l", xlab="interval", ylab="avg steps")
```


### Maximum interval: `r which.max(dailyavg)*5` th minute

## Imputing missing values

### NA values are imputed by the mean across all days

```{r echo="true"}
nas<-is.na(DT$steps)
DTimp<-DT
DTimp[nas,"steps"]<-mean(steps, na.rm="true")
```
### Calculate histogram, mean and median with imputed dataset

```{r echo="true"}
steps2<-by(DTimp$steps, DTimp$date, function(x) sum(x))
hist(steps2)
```

### Mean number of steps per day : `r mean(steps2, na.rm="true")` Difference: `r mean(steps2, na.rm="true")-mean(steps, na.rm="true")`
### Median number of steps per day: `r median(steps2)` Difference: `r median(steps2, na.rm="true")-mean(steps, na.rm="true")`



## Are there differences in activity patterns between weekdays and weekends?

```{r echo="true"}
DTweekdays<-weekdays(as.Date(DT$date))
DTweekdays[DTweekdays=="Montag"]<-1
DTweekdays[DTweekdays=="Dienstag"]<-1
DTweekdays[DTweekdays=="Mittwoch"]<-1
DTweekdays[DTweekdays=="Donnerstag"]<-1
DTweekdays[DTweekdays=="Freitag"]<-1
DTweekdays[DTweekdays=="Samstag"]<-0
DTweekdays[DTweekdays=="Sonntag"]<-0
DT1<-cbind(DT,DTweekdays)
weekday<-DT1[DT1$DTweekdays==1,]
weekdayavg<-by(weekday$steps, weekday$interval, function(x) mean(x, na.rm="true"))
weekend<-DT1[DT1$DTweekdays==0,]
weekendavg<-by(weekend$steps, weekend$interval, function(x) mean(x, na.rm="true"))
par(mfrow=c(2,1)) 
plot(weekdayavg, type="l", xlab="interval weekday", ylab="avg steps", main="weekdays")
plot(weekendavg, type="l", xlab="interval weekend", ylab="avg steps", main="weekend")
```

###Yes there are differences
